Clicks and Cliques

### 2018-12-20 papersoul.Rnw
tidy life.tab chunk

d2 <- census.data %>% 
  select(aveageF, prop1821, Bachelor.s.degree.or.higher., gini , own.rate , afri.pro, prop.new.entry, un.rate, prop.no.workers ) %>%
  dist()

@@

\begin{figure}[hbpt]
<<cluster.plot2, dependson='data',echo=FALSE, fig.height=4,message=FALSE,warning=FALSE,warning=FALSE,fig.height=6.5>>=
ind <- colnames(soul.red2) == 'cl.id'
colnames(soul.red2)[ind] <- 'Cluster.ID'

prodplot(soul.red2, PROJWT ~ CCEGRP2+ Cluster.ID + YEAR, divider=c("vspine", "hspine",'vspine'), subset = level == 2)+aes(fill = CCEGRP2) + theme(legend.position = 'bottom', legend.title = element_blank(),axis.title.y=element_blank()) + scale_fill_brewer(type='seq', palette=1)

@@

### VARIFICAR NOMBRES REPETIDOS EN SVYVAR !!!!!!!
life <- svyby(~prop.res+QD1+CCE, ~QSB, des.wt, svymean, keep.var=TRUE, na.rm=T)
lifevar <- svyby(~prop.res+CCE, ~QSB, des.wt, svyvar, keep.var=TRUE, na.rm=T)
lifevar$rho <- with(lifevar, V2/sqrt(V1*V4))

qplot(data=life, x=prop.res, y=QSB, size=I(4), ylab='',xlab='Proportion of lifetime living in the community')+theme(axis.text.y = element_text( size=I(10)))
@
\caption{Dot chart of communities sorted from top to bottom by attachment against the mean proportion of lifetime spent in the current community (stay). Communities where most of people are living longer are the less attached ones. \label{stay}}
\end{figure}

<<life.tab, dependson=c('corplot','life'),echo=FALSE, results='asis', cache=FALSE>>=
aux1 <- subset(dat.cor, vars %in% c("prop.new.entry","av.rent","av.own" ) & type=='Attached')[,1:2]

rho <- with(life, round(cor(CCE, prop.res),2) )

aux2   <- data.frame(vars='stay', cor=rho)
aux3 <- rbind(aux1,aux2)
description <-c('Average years renting in current home', 'Average years owning the current home',
              'Prop. of people not borned in the community', 'Proportion of age in current comunity')
data.source <- c(rep('Census Bureau', 3), 'Knight-Gallup data')
tab <- data.frame(Data=data.source,Description=description,Correlation=aux3$cor)
row.names(tab) <- NULL
tab <- xtable(tab, caption='Correlation with attachment', label='lifetab')
print(tab, caption.placement='top')
@

>>>>

d2 <- census.data %>% 
  select(aveageF, prop1821, Bachelor.s.degree.or.higher., gini , own.rate , afri.prop, prop.new.entry, un.rate, prop.no.workers ) %>%
  dist()

@@

\begin{figure}[hbpt]
<<cluster.plot2, dependson='data',echo=FALSE, fig.height=4,message=FALSE,warning=FALSE,warning=FALSE,fig.height=6.5>>=

soul.red2 %>%  rename(Cluster.ID = cl.id ) %>% 
prodplot(PROJWT ~ CCEGRP2 + Cluster.ID + YEAR, divider = c("vspine", "hspine",'vspine'), subset = level == 2) + aes(fill = CCEGRP2) + theme(legend.position = 'bottom', legend.title = element_blank(),axis.title.y = element_blank()) + scale_fill_brewer(type='seq', palette = 1)

@@

### VARIFICAR NOMBRES REPETIDOS EN SVYVAR !!!!!!!
life <- svyby(~prop.res + QD1 + CCE, ~QSB, des.wt, svymean, keep.var = TRUE, na.rm = T)
lifevar <- svyby(~prop.res + CCE, ~QSB, des.wt, svyvar, keep.var = TRUE, na.rm = T)
lifevar$rho <- with(lifevar, V2/sqrt(V1*V4))

ggplot(data = life, aes(x = prop.res, y = QSB), size = I(4)) + geom_point() +
labs(y = '', x ='Proportion of lifetime living in the community') + 
  theme(axis.text.y = element_text( size=I(10)))
@
\caption{Dot chart of communities sorted from top to bottom by attachment against the mean proportion of lifetime spent in the current community (stay). Communities where most of people are living longer are the less attached ones. \label{stay}}
\end{figure}

<<life.tab, dependson=c('corplot','life'),echo=FALSE, results='asis', cache=FALSE>>=
# check correlation for prop.new.entry, should be 0.13
rho <- with(life, round(cor(CCE, prop.res),2) )

cors %>%  
  filter(vars %in% c("Prop.new.entry", "Average.years.rent.in.community", "Aver.years.own.in.community") &  type =='Attached' ) %>% 
  select(vars, vv) %>% rename(cor = vv) %>%
  bind_rows(data.frame(vars = 'stay', cor = rho)) %>% 
  mutate(Data =  c(rep('Census Bureau', 3), 'Knight-Gallup data'), 
         Description = c( 'Average years owning the current home', 
                          'Average years renting in current home', 
                          'Prop. of people not borned in the community', 
                          'Proportion of age in current comunity')) %>% 
  rename(Correlation = cor) %>% 
  select(Data, Description, Correlation) %>% 
  xtable( caption='Correlation with attachment', label='lifetab') %>% 
  print( caption.placement = 'top', include.rownames = FALSE)
